Reproducible Research Project 1
================================


###1.Loading and processing the data
Code:
```{r}
activity <- read.csv("C:/Users/Edward Wang/Desktop/activity.csv")
```


###2. What is mean total number of steps taken per day?
Code:
```{r meansteps}
data1 <- aggregate(activity$steps, by=list(activity$date), FUN=sum, na.rm = T)
names(data1) <- c("date", "steps.sum")

library(ggplot2)
qplot(steps.sum, data = data1)

mean(data1$steps.sum)
median(data1$steps.sum)
```


###3. What is the average daily activity pattern?
Code:
```{r}
data2 <- aggregate(activity$steps, by=list(activity$interval), FUN=mean, na.rm = T)
names(data2) <- c("interval", "steps.mean")
qplot(interval, steps.mean, data = data2, geom = "line")

data3 <- aggregate(activity$steps, by=list(activity$interval), FUN=sum, na.rm = T)
names(data3) <- c("interval", "steps.sum")
data3[data3$steps.sum == max(data3$steps.sum),]
```


###4. Imputing missing values
Code:
```{r}
table(is.na(activity$steps))

datawithoutna <- read.csv("C:/Users/Edward Wang/Desktop/activity.csv")
for (i in 1:length(datawithoutna$steps)) {
    if (is.na(datawithoutna$steps[i]) == T) {
      datawithoutna$steps[i] <- data2$steps.mean[data2$interval == datawithoutna$interval[i]]
    } 
  }

data4 <- aggregate(datawithoutna$steps, by=list(datawithoutna$date), FUN=sum)
names(data4) <- c("date", "steps.sum")

qplot(steps.sum, data = data4)
mean(data4$steps.sum)
median(data4$steps.sum)
```
Of course the mean and median value of this part is different from the ones in the first part because we filled the missing values with another value.


###5. Are there differences in activity patterns between weekdays and weekends?
Code:
```{r}
category <- c(1: length(datawithoutna$date))
datawithoutna <- cbind(datawithoutna, category)
for (i in 1:length(datawithoutna$date)) {
    if (weekdays(as.Date(datawithoutna$date[i])) == "ÐÇÆÚÁù") {
      datawithoutna$category[i] <- "Weekend"
    } else 
    if (weekdays(as.Date(datawithoutna$date[i])) == "ÐÇÆÚÈÕ") {
      datawithoutna$category[i] <- "Weekend"
    }
      else {
      datawithoutna$category[i] <- "Weekday"
    }
  }
datawithoutna$category <- factor(datawithoutna$category)

data5 <- aggregate(datawithoutna$steps, by=list(datawithoutna$interval, datawithoutna$category), FUN = mean)
names(data5) <- c("interval", "category", "steps.mean")
qplot(interval, steps.mean, data = data5, geom = "line", facets = category ~ .)
```

